---
title       : Quality Control and quality
subtitle    : Developing Data Products slide
author      : Maciej Czyżowicz
job         :
framework   : io2012 # {102012, html5slides, Shower, dzslides, . . .  
highlighter : highlight.js # {highlight.js, prettify, highlight} 
hitheme     : tomorrow # 
widgets     : [] # {mathjax, quiz, bootstrap}
mode        : selfcontained #I {Standalone, draft}

---

## Quality Control and quality assurance
 1. Very important in multiple (if not all) industries
 2. For most, this means that one or more people are meticulously inspecting what's coming out
 3. Looking for imperfections and validating that requirements for products and services produced are satisfied. 
 
## Enter statistical quality control

 1. Statistical process control (SPC) is a method of quality control which uses statistical methods. (http://en.wikipedia.org/wiki/Statistical_process_control)
 2. Especially a Shewhart individuals control chart

---

## Basic tools for working with qcc
 
```{r echo=TRUE}
library(qcc) # for creating qcc plots
library(xts) # for creating and working with time series
library(lubridate) # for parsing strings to dates
```

---

## QCC Shiny app

* App was created to be a demo of QCC abilities in R.
* It contains predefined set of observation spanning two years
* It displays a quality check and control plot
* Range of dates can be used to manipulate the chart
* Each time the date change (being range for base (reference) data or for new data) plot will update

## Apps avaliable at:
# http://czyzu.shinyapps.io/DevDataProd_Project

---

## Sample plot

```{r echo=FALSE}
observations<-read.csv('dol_1.csv', sep="\t")
rownames(observations) = observations[,1]
observations<-observations[, "COUNT", drop=FALSE]
observations.ts<-as.xts(observations)
dane_bazowe<-window(observations.ts, end=parse_date_time("2014-07-01", "%y-%m-%d"))
dane_testowe<-window(observations.ts, start=parse_date_time("2014-07-01", "%y-%m-%d"))
```
```{r  fig.align='center'}
qcc (data=dane_bazowe, newdata=dane_testowe, 
     type="xbar.one", title="Number of observations", xlab="day")
```

